### 2021-04-16 manuscript.rmd
Spell check with ispell, fix formatting issues

This study of ecological effect on individual behaviours has a long tradition in social sciences. A famous example was Émile Durkheim's investigation on the ecological factors associated with suicide [@durkheim1897suicide]. Durkheim found the higher suicide rate among citizens from Scandinvian countries than those from other European countries. Using today’s standard, Durkheim's analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative content analysis. An example of hypothesis-generating comparative content analysis is @chan2020combining, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized. Hypothesis-generating comparative content analysis, however, is rare. Most studies have a confirmatory outlook. As we see from the example hypotheses above, most of these studies propose hypotheses to test for ecological effects. In this context usually traditional (frequentist) hypothesis testing approaches were used: @esser:2013:C lumped multiple outlets from the same country together and then used univariate analysis of variance to test for the differences in the proportion of opinion-orienting articles across countries. In @wu:2000:SDI, multiple stepwise regression was used. These approaches violate the underlying assumptions of the statistical analyses. It highlights the fact that comparative content analysis introduces a feature that researchers usually overlook: media contents are clustered in multilevel. A news article is nested within its media outlet and its media outlet is in turn nested within its country. Theoretically with a large enough sample it can be argued that a news article is nested within authors. Such data structure brings two problems: non-atomicity and non-stochasticity.

@@

[^2]: Some communication researchers apply the disaggregation approach by justifying the intraclass correlation between groups is small and the impact of ignoring the multilevel structure is also small [a finding in @chen:2012:IIL], see an example in @zhu:2020:S [footnote 5]. Even a multilevel modeling textbook avocates this justification [@bickel2007multilevel]. We reject this justification because it violates the independence assumption and thus commits atomistic fallacy. See also @nezlek:2008:IMM for a criticism of such justification.

There are two solutions to this. The first solution is to aggregate the micro-level dependent variable across a macro-level inpendent variable. Suppose there are $n$ countries in the above example. One can aggregate the total number of articles covering China as $z_{k}$ for the $k$-th country, where $k=i,\ldots,n$. Then, we can do a count-based regression with a regression equation like so:

@@

Using this aggregation method, the unit of analysis effectively switches from article to country. This method is useful when $x$ is the only independent variable, akin @esser:2013:C. It is not technically committing atomistic fallacy, when one uses the value of slope as the evidence for an ecological effect. However, this method still has important drawbacks. First, it cannot be used for data with more than two levels. In @esser:2013:C, for example, multiple media outlets from the same country were lumped together and in effect, assumed to be homogenous and the information about media outlets was discarded. Second, this method discards a massive amount of information. It is better for analysis of a dependent micro-level variable with a reasonably aggregation function (e.g. counting a binary variable). For numerical variables, aggregation functions such as taking a mean or median cannot capture the spread of the micro-level variable [@bryk:1988:H]. Also, the effective sample size is reduced from the number of articles ($m$) to the number of countries ($n$). Nonetheless, this aggregation method, although inflexible, is still useful when the number of groups (e.g. $n$) is large. It is also useful to collapse micro-levels (e.g. article-level) that are not useful in answering one’s research questions.

@@

Following arguments from @western:1994:BIC and @stegmueller:2013:HMC for comparative studies, Bayesian inference should be used for analyzing data from comparative content analysis. Choosing a Bayesian approach also solves the problem of misinterpreted confidence intervals Hoeckstra et al., 2014; Rinke & Schneider, 2016). Switching to a Bayesian approach addresses this issue as Bayesian „credible intervals support an interpretation of probability in terms of plausibility" (Morey et al., 2016, p. 120). However, for Bayesian models priors have to be chosen by reserachers.

@@

We skip elaborating part 1, because some, but certainty not all, researchers have the means to amass a massive amount. The mechanism of how part 2 can be used to derive the likelihood function is beyond the scope of this paper. <!-- We provide a tutorial in Appendix I(+++TODO) for those who want to get an intuition. --> The current standard method, MCMC, is much more computationally intensive and has only been possible on desktop computer since mid-1990s [@robert:2011:SHM]. And only in the last few years that can be done efficiently [@hoffman2014no], thanks to the probablistic programming language *Stan* [@gelman:2015:S]. R interfaces to Stan, such as *brms* [@burkner2017advanced], make Bayesian analysis even more accessible to R users. But still, it is important to be mindful that Bayesian analysis is much more computational intensive than methods such as MLE. Our benchmark suggests that Bayesian analysis needs at least 100 times more running time than MLE.

@@

*"There is a general challenge to a prescription of more widespread use of Bayesian methods for multilevel modelling, and that is that such methods require statistical expertise beyond that of most applied social science researchers, as well as specialist software (or software with which such researchers are unfamiliar)."* @bryan:2015:MMC [p. 19]

Bayesian analysis is still a minority statistical method in social sciences. It is reasonable to say that Bayesian analysis is extremely rare in our field. Although some communication researchers adopted the method [e.g. @kovic:2017:B;@chan2020high] these studies are not comparative. As far as we know, the only available comparative content analysis that Bayesian multilevel regression was used for studying ecological effect is @leeuw:2020:AAT. We believe comparative content analysis fits the use case of Bayesian multilevel regression analysis. Although there is another methodological introduction to Bayesian analysis aiming at communication researchers [@konijn:2015:PSP], the main purpose of this paper is to demonstrate how to practically implement one using the R package *brms* [@burkner2017advanced]. As the interface of *brms* is almost the same as *lme4* [@bates:2015:FLM, another R package for fitting multilevel models using MLE], *lme4* users might find *brms* extremely familiar. The above quoted challenge about the prescription of more widespread use of Bayesian methods for multilevel modelling is no longer an issue.

@@

We used only the data from 2019 as the baseline. It is important to note that the Hong Kong protests, the 30th anniversary of the Tiananmen Square Protests and the 70th anniversary of the communist regime were in that year. Also, it was in the zenith of the US-China trade war.

@@

A dictionary-based approach was used. The seed English and German dictionaries from the R package newsmap [@watanabe:2017:N] were used as the basis. The seed dictionaries contain words about Chinese, China, Beijing and Shanghai. We developed further the Spanish, Romanian, Korean, Portugese, Norwegian, and Dutch dictionaries. The dictionaries were applied to the 61 DTMs of all included media outlets. An article is classified as China coverage when at least one dictionary match is detected.

@@

```r
# brms
brms::brm(z ~ offset(log(n)) + (1|k)+log(x),
          family = negbinomial(), data = outlet_data)
# lme4
lme4::glmer.nb(z ~ offset(log(n)) + (1|k) + log(x), data = outlet_data)
```

@@

```r
MASS::glm.nb(z ~ offset(log(n)) + log(x), data = outlet_data)
```

@@

```r
brms::brm(y~(1|k/j)+log(x), family = bernoulli(), data = article_data)
lme4::glmmer(y~(1|k/j)+log(x), family = binomial(), data = article_data)
```

@@

```r
MASS::glm(y ~ log(x), family = binomial(), data = article_data)
```

@@

For the outlet-level analysis, there are four unknown parameters to be estimated: $\gamma_{00}$, $\mu_{0k}$, $\gamma_{01}$ and the negative binomial shape parameter $\phi$. For the article-level analysis, the four unknown paramters are $\gamma_{000}$, $\mu_{00k}$, $\gamma_{001}$ amd $\mu_{0j}$. The idea of choosing priors is to select a probable probability distribution for each of these unknown parameters.

@@

```r
weaklyinformative_prior <- c(prior_string("normal(0, 1)",
                                          class = "b"),
                             prior_string("normal(0, 1)",
                                          class = "Intercept"))
# The sample_prior argument is optional. But useful for further analysis.
import_brms <- brms::brm(z~offset(log(n))+(1|k)+log(x_import),
          data = outlet_data, family = negbinomial(),
          prior = weaklyinformative_prior, sample_prior = TRUE)
import_brms
```

@@

[^5]: HDI is one representation of Bayesian credible interval. It is important to note that, like confidence interval, there should be no "correct" choice of the level of credibility, but some established conventions. We choose, like many published works [e.g. @stegmueller:2013:HMC; @kovic:2017:B; @chan2020high], the default value of 95\% is to maintain "compatibility" with traditional approach of reporting 95\% confidence interval. However, there is a general concern about this crediblity level as being unstable for Bayesian analysis [@kruschke2014doing]. Some Bayesians, notably, Andrew Gelman, reports very liberal 50\% credible intervals. @mcelreath2020statistical selects 89\% to show the arbitariness of the practice. @leeuw:2020:AAT select 90\%.

Consistently, point estimates are remarkably similar. Bayesian multilevel regression gave a wider 95% HDI than confidence intervals from frequentist methods. It is similar to previous studies [@stegmueller:2013:HMC; @elff:2020:MAF]. The results indicate that only a higher export or import volume with China and the host country of the media outlet is associated with more reporting China. While the frequentist confidence intervals and the Bayesian credible interval seem to be similar, they are from a philosophical point of view totally different and lead to different forms of infference. The Bayesian approach alloows us to say that *given the observed data, the true estimate of log import volume has 95% probability of falling witin  0.18 and 0.33*. In contrast, the frequentist confidence interval only allows us to say that *when computing a confidence interval from the same type of data in repeated studies, 95% of the confidence intervals will include the true estimate of log import volume*. One of the misconceptions of frequentist confidence intervals is that they can be interpreted in a Bayesian way [@morey:2015]. This example illustrates that a Bayesian approach allows us to interpret the results in a more intutitive way.

@@

```{r fig1, echo = FALSE, fig.cap = "The right panel in the MCMC trace plot from plot() function showing the fuzzy catepillar pattern."}
require(brms)
import_brms <- readRDS("import_brms.RDS")
plot(import_brms)
```

@@

Instead of arguing the advatnages of Bayesian multilevel regression analysis once again like we did in the introduction, we propose several extensions to the above barebone analysis. The analyses in these extensions are not preregistered.

@@

```r
# suppose "public" is a binary variable
import_brms_public <- brms::brm(
      z~offset(log(n))+(1 + public|k)+log(x_import)*public,
      data = outlet_data, family = negbinomial(),
      prior = weaklyinformative_prior, sample_prior = TRUE)
import_brms_public
```

The regression coefficients for the main effect of public broadcasting and the interaction terms have a wide 95\% HDI that covers zero. It can be visualized with a conditional effects plot (Figure \@ref(fig:fig4), using the *conditional_effects()* function). The trajectories of public broadcastors and for-profit media outlets are similar, indicating no interaction.

@@

In this paper, we argue the case for using Bayesian multilevel regression analysis to analyse data from comparative content analyses. We demonstrate using the openly available useNews dataset that Bayesian analysis provides valid inference of ecological effects and can be done easily with the R package *brms*. Using a Bayesian approach, however, has also clearly some disadvantages. Reserachers have to define priors in order to run a Bayesian regression analysis. As we could show this limitation does not pose a controversial challenge as weakly informative prios can be chosen and in most cases enough data is available and thus the priors have almost no influence on the posterior distribution of the parameters. If we have prior knowledge it allows us to create even better models. Furthermore, it takes more time to get the results of a Bayesian regression analysis. Estimating a Bayesian regression model is a computationally demanding task. It took 4 days on a regular computer to get the results of the Bayesian regression model with 1,525,871 articles (Model B1). Still, eventually it worked and typical studies in comparative journalism research [e.g. 6525 articles in @esser:2013:C] can be estimated in a reasonable time [^TIME].

[^TIME]: We benchmarked the same model but with a random subset of data of some more "typical" sample sizes. A model with a large sample size of 30,000 can be estimated in less than 17 minutes on a typical computer with 6 cores. Although it is comparatively more computational intensive than lme4, the time needed is still reasonable.

>>>>

This study of ecological effect on individual behaviors has a long tradition in social sciences. A famous example was Émile Durkheim's investigation on the ecological factors associated with suicide [@durkheim1897suicide]. Durkheim found the higher suicide rate among citizens from Scandinavian countries than those from other European countries. Using today’s standard, Durkheim's analysis is descriptive and this descriptive approach for studying ecological effect is indeed still useful for hypothesis generation in comparative content analysis. An example of hypothesis-generating comparative content analysis is @chan2020combining, in which the sentiment profiles of terrorism coverage from Muslim- and Christian-majority countries were visualized. Hypothesis-generating comparative content analysis, however, is rare. Most studies have a confirmatory outlook. As we see from the example hypotheses above, most of these studies propose hypotheses to test for ecological effects. In this context usually traditional (frequentist) hypothesis testing approaches were used: @esser:2013:C lumped multiple outlets from the same country together and then used univariate analysis of variance to test for the differences in the proportion of opinion-orienting articles across countries. In @wu:2000:SDI, multiple stepwise regression was used. These approaches violate the underlying assumptions of the statistical analyses. It highlights the fact that comparative content analysis introduces a feature that researchers usually overlook: media contents are clustered in multilevel. A news article is nested within its media outlet and its media outlet is in turn nested within its country. Theoretically with a large enough sample it can be argued that a news article is nested within authors. Such data structure brings two problems: non-atomicity and non-stochasticity.

@@

[^2]: Some communication researchers apply the disaggregation approach by justifying the intraclass correlation between groups is small and the impact of ignoring the multilevel structure is also small [a finding in @chen:2012:IIL], see an example in @zhu:2020:S [footnote 5]. Even a multilevel modeling textbook advocates this justification [@bickel2007multilevel]. We reject this justification because it violates the independence assumption and thus commits atomistic fallacy. See also @nezlek:2008:IMM for a criticism of such justification.

There are two solutions to this. The first solution is to aggregate the micro-level dependent variable across a macro-level independent variable. Suppose there are $n$ countries in the above example. One can aggregate the total number of articles covering China as $z_{k}$ for the $k$-th country, where $k=i,\ldots,n$. Then, we can do a count-based regression with a regression equation like so:

@@

Using this aggregation method, the unit of analysis effectively switches from article to country. This method is useful when $x$ is the only independent variable, akin @esser:2013:C. It is not technically committing atomistic fallacy, when one uses the value of slope as the evidence for an ecological effect. However, this method still has important drawbacks. First, it cannot be used for data with more than two levels. In @esser:2013:C, for example, multiple media outlets from the same country were lumped together and in effect, assumed to be homogeneous and the information about media outlets was discarded. Second, this method discards a massive amount of information. It is better for analysis of a dependent micro-level variable with a reasonably aggregation function (e.g. counting a binary variable). For numerical variables, aggregation functions such as taking a mean or median cannot capture the spread of the micro-level variable [@bryk:1988:H]. Also, the effective sample size is reduced from the number of articles ($m$) to the number of countries ($n$). Nonetheless, this aggregation method, although inflexible, is still useful when the number of groups (e.g. $n$) is large. It is also useful to collapse micro-levels (e.g. article-level) that are not useful in answering one’s research questions.

@@

Following arguments from @western:1994:BIC and @stegmueller:2013:HMC for comparative studies, Bayesian inference should be used for analyzing data from comparative content analysis. Choosing a Bayesian approach also solves the problem of misinterpreted confidence intervals [@hoekstra:2014:R;@rinke:2018:PMA]. Switching to a Bayesian approach addresses this issue as Bayesian "credible intervals support an interpretation of probability in terms of plausibility" [@morey:2015, p.120]. However, for Bayesian models priors have to be chosen by researchers.

@@

We skip elaborating part 1, because some, but certainty not all, researchers have the means to amass a massive amount. The mechanism of how part 2 can be used to derive the likelihood function is beyond the scope of this paper. <!-- We provide a tutorial in Appendix I(+++TODO) for those who want to get an intuition. --> The current standard method, MCMC, is much more computationally intensive and has only been possible on desktop computer since mid-1990s [@robert:2011:SHM]. And only in the last few years that can be done efficiently [@hoffman2014no], thanks to the probabilistic programming language *Stan* [@gelman:2015:S]. R interfaces to Stan, such as *brms* [@burkner2017advanced], make Bayesian analysis even more accessible to R users. But still, it is important to be mindful that Bayesian analysis is much more computational intensive than methods such as MLE. Our benchmark suggests that Bayesian analysis needs at least 100 times more running time than MLE.

@@

*"There is a general challenge to a prescription of more widespread use of Bayesian methods for multilevel modeling, and that is that such methods require statistical expertise beyond that of most applied social science researchers, as well as specialist software (or software with which such researchers are unfamiliar)."* @bryan:2015:MMC [p. 19]

Bayesian analysis is still a minority statistical method in social sciences. It is reasonable to say that Bayesian analysis is extremely rare in our field. Although some communication researchers adopted the method [e.g. @kovic:2017:B;@chan2020high] these studies are not comparative. As far as we know, the only available comparative content analysis that Bayesian multilevel regression was used for studying ecological effect is @leeuw:2020:AAT. We believe comparative content analysis fits the use case of Bayesian multilevel regression analysis. Although there is another methodological introduction to Bayesian analysis aiming at communication researchers [@konijn:2015:PSP], the main purpose of this paper is to demonstrate how to practically implement one using the R package *brms* [@burkner2017advanced]. As the interface of *brms* is almost the same as *lme4* [@bates:2015:FLM, another R package for fitting multilevel models using MLE], *lme4* users might find *brms* extremely familiar. The above quoted challenge about the prescription of more widespread use of Bayesian methods for multilevel modeling is no longer an issue.

@@

We used only the data from 2019 as the baseline. It is important to note that the Hong Kong protests, the 30th anniversary of the Tienanmen Square Protests and the 70th anniversary of the communist regime were in that year. Also, it was in the zenith of the US-China trade war.

@@

A dictionary-based approach was used. The seed English and German dictionaries from the R package newsmap [@watanabe:2017:N] were used as the basis. The seed dictionaries contain words about Chinese, China, Beijing and Shanghai. We developed further the Spanish, Romanian, Korean, Portuguese, Norwegian, and Dutch dictionaries. The dictionaries were applied to the 61 DTMs of all included media outlets. An article is classified as China coverage when at least one dictionary match is detected.

@@

```r
require(brms)
require(lme4)
# brms
brm(z ~ offset(log(n)) + (1|k)+log(x),
          family = negbinomial(), data = outlet_data)
# lme4
glmer.nb(z ~ offset(log(n)) + (1|k) + log(x), data = outlet_data)
```

@@

```r
require(MASS)
glm.nb(z ~ offset(log(n)) + log(x), data = outlet_data)
```

@@

```r
brm(y~(1|k/j)+log(x), family = bernoulli(), data = article_data)
glmmer(y~(1|k/j)+log(x), family = binomial(), data = article_data)
```

@@

```r
glm(y ~ log(x), family = binomial(), data = article_data)
```

@@

For the outlet-level analysis, there are four unknown parameters to be estimated: $\gamma_{00}$, $\mu_{0k}$, $\gamma_{01}$ and the negative binomial shape parameter $\phi$. For the article-level analysis, the four unknown parameters are $\gamma_{000}$, $\mu_{00k}$, $\gamma_{001}$ amd $\mu_{0j}$. The idea of choosing priors is to select a probable probability distribution for each of these unknown parameters.

@@

```r
weaklyinformative_prior <- c(prior_string("normal(0, 1)",
                                          class = "b"),
                             prior_string("normal(0, 1)",
                                          class = "Intercept"))
# The sample_prior argument is optional. But useful for further analysis.
import_brms <- brm(z~offset(log(n))+(1|k)+log(x_import),
          data = outlet_data, family = negbinomial(),
          prior = weaklyinformative_prior, sample_prior = TRUE)
import_brms
```

@@

[^5]: HDI is one representation of Bayesian credible interval. It is important to note that, like confidence interval, there should be no "correct" choice of the level of credibility, but some established conventions. We choose, like many published works [e.g. @stegmueller:2013:HMC; @kovic:2017:B; @chan2020high], the default value of 95\% is to maintain "compatibility" with traditional approach of reporting 95\% confidence interval. However, there is a general concern about this credibility level as being unstable for Bayesian analysis [@kruschke2014doing]. Some Bayesians, notably, Andrew Gelman, reports very liberal 50\% credible intervals. @mcelreath2020statistical selects 89\% to show the arbitrariness of the practice. @leeuw:2020:AAT select 90\%.

Consistently, point estimates are remarkably similar. Bayesian multilevel regression gave a wider 95% HDI than confidence intervals from frequentist methods. It is similar to previous studies [@stegmueller:2013:HMC; @elff:2020:MAF]. The results indicate that only a higher export or import volume with China and the host country of the media outlet is associated with more reporting China. While the frequentist confidence intervals and the Bayesian credible interval seem to be similar, they are from a philosophical point of view totally different and lead to different forms of inference. The Bayesian approach allows us to say that *given the observed data, the true estimate of log import volume has 95% probability of falling within  0.18 and 0.33*. In contrast, the frequentist confidence interval only allows us to say that *when computing a confidence interval from the same type of data in repeated studies, 95% of the confidence intervals will include the true estimate of log import volume*. One of the misconceptions of frequentist confidence intervals is that they can be interpreted in a Bayesian way [@morey:2015]. This example illustrates that a Bayesian approach allows us to interpret the results in a more intuitive way.

@@

```{r fig1, echo = FALSE, fig.cap = "The right panel in the MCMC trace plot from plot() function showing the fuzzy caterpillar pattern."}
require(brms)
import_brms <- readRDS("import_brms.RDS")
plot(import_brms)
```

@@

Instead of arguing the advantages of Bayesian multilevel regression analysis once again like we did in the introduction, we propose several extensions to the above barebone analysis. The analyses in these extensions are not preregistered.

@@

```r
# suppose "public" is a binary variable
import_brms_public <- brm(
      z~offset(log(n))+(1 + public|k)+log(x_import)*public,
      data = outlet_data, family = negbinomial(),
      prior = weaklyinformative_prior, sample_prior = TRUE)
import_brms_public
```

The regression coefficients for the main effect of public broadcasting and the interaction terms have a wide 95\% HDI that covers zero. It can be visualized with a conditional effects plot (Figure \@ref(fig:fig4), using the *conditional_effects()* function). The trajectories of public broadcasters and for-profit media outlets are similar, indicating no interaction.

@@

In this paper, we argue the case for using Bayesian multilevel regression analysis to analyze data from comparative content analyses. We demonstrate using the openly available useNews dataset that Bayesian analysis provides valid inference of ecological effects and can be done easily with the R package *brms*. Using a Bayesian approach, however, has also clearly some disadvantages. Researchers have to define priors in order to run a Bayesian regression analysis. As we could show this limitation does not pose a controversial challenge as weakly informative priors can be chosen and in most cases enough data is available and thus the priors have almost no influence on the posterior distribution of the parameters. If we have prior knowledge it allows us to create even better models. Furthermore, it takes more time to get the results of a Bayesian regression analysis. Estimating a Bayesian regression model is a computationally demanding task. It took 4 days on a regular computer to get the results of the Bayesian regression model with 1,525,871 articles (Model B1). Still, eventually it worked and typical studies in comparative journalism research [e.g. 6525 articles in @esser:2013:C] can be estimated in a reasonable time frame [^TIME].

[^TIME]: We benchmarked the same model B1 but with subsets of data of some more "typical" sample sizes. A model with a large sample size of 30,000 can be estimated in less than 17 minutes on a typical 6-core computer. Although it is comparatively more computational intensive than *lme4*, the time needed is still reasonable.
